Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-11 paper.tex
Define "commutativity" for applicative functors
Reviewer C:
  l. 212 : « commutative », je ne comprends pas ce qui est commutatif ici?
Clarify semantics of `perm`
Reviewer C:
  l. 295 : la permutation est fixée, serait-il possible d'utiliser une permutation quelconque?

Indeed, aside from the logical operations, the rotations are in fact
almost free thanks to the \textsc{Arm} Cortex barrel
shifter.

>>>>

Indeed, aside from the logical operations, the rotations are in fact
almost free thanks to the \textsc{Arm} Cortex barrel
shifter.\footnote{By this remark, we hope to have established our
credentials as budding cryptographers.}
